---
title: "Homework 6"
author: "Anya Steinhart"
date: "February 21, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
z <- read.table("AprilData.csv",header=TRUE,sep=",", stringsAsFactors=FALSE)
str(z)
summary(z)
head(z)
```
 
```{r}
library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation
```
 
##Plot histogram of data 
```{r}
p1 <- ggplot(data=z, aes(x=BodyLength, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2)
print(p1)
```

##Add empirical density curve 
```{r}
p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
print(p1)
 
```

##Get maximum likelihood parameters for normal 
```{r}
normPars <- fitdistr(z$BodyLength,"normal")
print(normPars)
 
```
 
```{r}
str(normPars)
```
 
```{r}
normPars$estimate["mean"]
```
##Plot Normal Probabilty Density 
```{r}
meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]
 
xval <- seq(0,max(z$BodyLength),len=length(z$BodyLength))
 
stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(z$BodyLength), args = list(mean = meanML, sd = sdML))
p1 + stat
 
```
####Plot Exponential Probability
```{r}
expoPars <- fitdistr(z$BodyLength,"exponential")
rateML <- expoPars$estimate["rate"]
 
stat2 <- stat_function(aes(x = xval, y = ..y..), fun = dexp, colour="blue", n = length(z$BodyLength), args = list(rate=rateML))
p1 + stat + stat2
```
##Plot Uniform Probabilty Density
```{r}
stat3 <- stat_function(aes(x = xval, y = ..y..), fun = dunif, colour="darkgreen", n = length(z$BodyLength), args = list(min=min(z$BodyLength), max=max(z$BodyLength)))
 p1 + stat + stat2 + stat3

```

##Plot Gamma Probability Density 
```{r}
gammaPars <- fitdistr(z$BodyLength,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="brown", n = length(z$BodyLength), args = list(shape=shapeML, rate=rateML))
 p1 + stat + stat2 + stat3 + stat4
```

##Plot Beta Probability Desity 
```{r}
pSpecial <- ggplot(data=z, aes(x=BodyLength/(max(BodyLength + 0.1)), y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
  xlim(c(0,1)) +
  geom_density(size=0.75,linetype="dotted")

betaPars <- fitdistr(x=z$BodyLength/max(z$BodyLength + 0.1),start=list(shape1=1,shape2=2),"beta")
shape1ML <- betaPars$estimate["shape1"]
shape2ML <- betaPars$estimate["shape2"]

statSpecial <- stat_function(aes(x = xval, y = ..y..), fun = dbeta, colour="orchid", n = length(z$BodyLength), args = list(shape1=shape1ML,shape2=shape2ML))
pSpecial + statSpecial
```

###What Works the Best
The best fitting distribution was the normal distribution 

##Simulated Beta Distribution 
```{R}
x <-as.data.frame(rnorm(n=120,mean=270.42,sd=46.864135))

names(x) <- "BodyLength"
#x <- x[x$BodyLength>0,]
str(x)

p1 <- ggplot(data=x, aes(x=BodyLength, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(p1)

normPars <- fitdistr(x$BodyLength,"normal")
print(normPars)


meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(x$BodyLength),len=length(x$BodyLength))

stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(x$BodyLength), args = list(mean = meanML, sd = sdML))
 p1 + stat
``` 

##New Histogram 
```{r} 
p1 <- ggplot(data=z, aes(x=BodyLength, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2)
print(p1) 
normPars <- fitdistr(z$BodyLength,"normal")
print(normPars)

meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]
 
xval <- seq(0,max(z$BodyLength),len=length(z$BodyLength))
 
stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(z$BodyLength), args = list(mean = meanML, sd = sdML))
p1 + stat
```

##How do the two histogram profiles compare? Do you think the model is doing a good job of simulating realistic data that match your original measurements? Why or why not. 
The simulated data fit the density curve better than the actual data. The simulated peaked where the curve peaked. In reality, the larval lengths peaked twice, and had a low where the curve peaked. The simulation cleaned the data up, and made the histogram more aesthetically pleasing, but it doens't match the real data. 
