---
title: "Homework 7"
author: "Anya Steinhart"
date: "February 28, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###1.Function to create data 
```{r}
dataCreate <- function(mean1=317.59, mean2=235.38, n1=60, n2=60, sd1=30.58, sd2=30.18){
  mydf <- data.frame(control=rnorm(mean = mean1, n=n1, sd=sd1), test=rnorm(mean=mean2, n=n2, sd=sd2))
  return(mydf)
}
myDF <-dataCreate(mean1=317.59)
head(myDF)


```
###2. Function for ANOVA
```{r}
library(reshape2)

myDF2 <- melt(myDF) 
ANOVA <- function(data=myDF2){
  myANOVA <- aov(value~variable, data=data)
  summary(myANOVA)
}

ANOVA(data=myDF2)
ANOVA()
myANOVA <- aov(value~variable, data=myDF2)
summary(myANOVA)
```
###3. Function to create box plot 
```{r}

library(ggplot2)
urchinBOXPLOT <- function(data=myDF2){
  ggplot(data=data,aes(x=variable, y=value, fill=variable)) + geom_boxplot()
}
urchinBOXPLOT()
```

###Attempts at running anova with different values
#####Changing the means 
```{r}
df5 <- dataCreate(mean1=375.28, mean2=375.5)
df5<-melt(df5)
ANOVA(data=df5)
urchinBOXPLOT(df5)
```

```{r}
df6 <- dataCreate(mean1 = 100, mean2 = 780)
df6 <- melt(df6)
ANOVA(data=df6)
urchinBOXPLOT(df6)
```

### Changing the Standard Deviation 
```{r}
df7<- dataCreate (sd1 = 10, sd2 = 75)
df7 <- melt(df7)
ANOVA(data=df7)
urchinBOXPLOT(df7)

```

### Changing the sampling size 
```{r}
df8<- dataCreate (n1 = 10, n2= 10)
df8 <- melt(df8)
ANOVA(data=df8)
urchinBOXPLOT(df8)
```

###Summary 
When the *mean* of the control data and the treatment data are similar or almost the same, the p value between of these data increases closer to zero. As the means between the control and the treaments grow apart from each other, the p value decreases, showing there is a significant difference between the sets. As the *Standard deviation* increases between the sets, the p value also decreases. These changes are visible in the box plots. However, I thought that decreasing the *sampling size* would increase the p value. When I changed the sampling size, the p value became more significant than before. 


### Different Distribution- Uniform Distrubution 

```{r}
dataCreate2 <- function(min1=180.44, min2=250.12, n1=60, n2=60, max1=304.72, max2=395.45){
  mydf <- data.frame(control=runif(min = min1, n=n1, max=max1), test=runif(min=min2, n=n2, max=max2))
  return(mydf)
}
myDFU <-dataCreate2(min1=180.44)
head(myDFU)

```

#New ANOVA Function 
```{r}
library(reshape2)
myDFU2 <- melt(myDFU) 
ANOVA <- function(data=myDFU2){
  myANOVA <- aov(value~variable, data=data)
  summary(myANOVA)
}

ANOVA(data=myDFU2)
ANOVA()
myANOVA <- aov(value~variable, data=myDFU2)
summary(myANOVA)
```

### New Box Plot Function
```{r}
library(ggplot2)
urchinBOXPLOT <- function(data=myDFU2){
  ggplot(data=data,aes(x=variable, y=value, fill=variable)) + geom_boxplot()
}
urchinBOXPLOT()
```

### Running New ANOVAs. Changing Minimums and Maximums 
```{r}
dfU3 <- dataCreate2 (min1 = 100, min2 = 100)
dfU3 <- melt(dfU3)
ANOVA(data=dfU3)
urchinBOXPLOT(dfU3)

dfU5 <- dataCreate2 (min1 = 250, min2 = 250)
dfU5 <- melt(dfU5)
ANOVA(data=dfU5)
urchinBOXPLOT(dfU5)
```
#Changing the treatment size
```{r}
dfU6 <- dataCreate2 (n1 = 4, n2 = 4)
dfU6 <- melt(dfU6)
ANOVA(data=dfU6)
urchinBOXPLOT(dfU6)
```

#Changing both minimum and maximum
```{r}
dfU4 <- dataCreate2 (min1 = 100, min2 = 100, max1 = 300, max2 = 300)
dfU4 <- melt(dfU4)
ANOVA(data=dfU4)
urchinBOXPLOT(dfU4)
```

####Summary 
Setting the minimums to the same value, but keeping the maximums the same intial value originally placed in the function, results in an increase of the p value. However, the p value was still very significant. As expected, the p value increased to insignificantance when the minumum and maximum values of the control and treament data are set to be equal. Decrease the sample size resulted in an increased p value, while increased sample size resulted in a decreased p value. 